Stability in human interaction networks: primitive typology of vertex, prominence of measures and time activity statistics

### 2015-04-17 paper.tex
feita tabela inline, adiantado processo
adicionadas tabelas no corpo do artigo

@@

\begin{table*}[t]
	\caption{The rescaled circular mean $\theta_\mu'$, the standard deviation $S(z)$, the variance $Var(z)$, the circular dispersion $\delta(z)$ and the relation of maximum and minimum incidence at each time unit $\frac{max(incidence}{min(incidence}$. The Section~\ref{sec:mtime} exposes the theoretical background considered of directional (or circular) statistics.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c|c|c| }
        \hline
	scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{max(incidence)}{min(incidence)}$ \\ \hline\hline
	\input{tables/tab2TimeLAU}
    \end{tabular}
\end{center}
\label{tab:circ}
\end{table*}

@@

@@

@@

@@

@@

\subsection{Variance prevalence of centrality over symmetry and symmetry over clusterization}\label{prevalence}
The topology was analyzed using standard, well-established metrics of centrality and clustering.
We also introduced symmetry measures because there is evidence that they are relevant in social contexts~\cite{newmanEvolving}.
The contribution from the distinct metrics to network topology is very similar for all the networks, and did not vary with time.
This stability in network behavior is remarkable, as can be noticed by the small standard deviations of the contribution of each metric to principal components (from usual Principal Component Analysis~\cite{pca}) along time of Tables~\ref{compPCA0}-\ref{compPCA2}.

@@

    \subsection{Primitive typology from Erd\"os sectors}\label{sec:pty}
Consider the sector to which a participant belongs as her/his type. General considerations of this typology are:
\begin{itemize}
	\item A participant belongs to many networks (his family, family of a friend, the email list to which he belongs, work friends, etc.).
	\item A participant might belong to all three sectors at the same time. Actually, it is reasonable to assume that almost every person belongs to all three sectors for some of the networks.
	\item It is given by construction that a participant is of just one type at a network in a given snapshot (exception for the compound inclusive and exclusive criterion given in Section~\ref{sectioning}).
	\item The participant often transitions from one sector to another within a network.
	\item Reported stability of network structure arises from activity with continuous change of the participant types.
	\item Type often changes with the scale of the activity window. For example, two snapshots of 200 and 10000 messages will probably reveal participants with more than one type. 
\end{itemize}

>>>>

\begin{table}[!h!]
    \caption{Distribution of activity among agents. First column is dedicated to percentage of messages sent by the most active participant. Column for the first quartile ($1Q$) exhibits minimum percentage of participants responsible for at least 25\% of total messages. Similarly, the column for the first three quartiles $1-3Q$ exhibits minimum percentage of participants responsible for 75\% of total messages. The last decile $-10D$ column has maximum percentage of participants responsible for 10\% of messages.}
\begin{center}
    \begin{tabular}{ | l ||  c | c | c | c | }
        \hline
        list & hub & $ 1Q $ & $ 1-3Q $ & $-10D$ \\ \hline
	\input{tables/userTab}
    \end{tabular}
\end{center}
\label{autores}
\end{table}

@@

\begin{table*}[t]
	\caption{The rescaled circular mean $\theta_\mu'$, the standard deviation $S(z)$, the variance $Var(z)$, the circular dispersion $\delta(z)$ and the relation of maximum and minimum incidence at each time unit $\frac{max(incidence}{min(incidence}$. The Section~\ref{sec:mtime} exposes the theoretical background considered of directional (or circular) statistics.}
\begin{center}
    \begin{tabular}{ |l|| c|c|c|c|c| }
        \hline
	scale & $\theta_\mu'$ & $S(z)$ & $Var(z)$ & $\delta(z)$ & $\frac{max(incidence)}{min(incidence)}$ \\ \hline\hline
	\input{tables/tab2TimeCPP}
    \end{tabular}
\end{center}
\label{tab:circ}
\end{table*}

@@

\begin{table}[!h]
	\caption{.}
	\footnotesize
	\input{tables/tabHoursCPP_}
\label{tab:hin}
\end{table}

@@

\begin{table}[h]
	\caption{.}
\begin{center}
    \begin{tabular}{ | l |  c | c | c | c | c |   c | c |}
        \hline
        & Mon & Tue & Wed & Thu & Fri & Sat & Sun  \\ \hline
	\input{tables/tabWeekdays}
    \end{tabular}
\end{center}
\label{tab:win}
\end{table}

@@

\begin{table}[!h]
	\caption{.}
	\footnotesize
	\input{tables/tabMonthdaysCPP}
\label{tab:min}
\end{table}

@@

\begin{table}[!h]
	\caption{.}
	\footnotesize
	\input{tables/tabMonthsLAD}
\label{tab:min}
\end{table}

@@

\subsection{Variance prevalence of centrality over symmetry and symmetry over clusterization}\label{prevalence}
The topology was analyzed using standard, well-established metrics of centrality and clustering.
We also introduced symmetry measures because there is evidence that they are relevant in social contexts~\cite{newmanEvolving}.
The contribution from the distinct metrics to network topology is very similar for all the networks, and did not vary with time.
This stability in network behavior is remarkable, with small standard deviations of the contribution of each metric to principal components in all lists analyzed. Table~\ref{fig:pcain} exemplifies the principal components formation with all measures considered, while Tables~\ref{compPCA0}-\ref{compPCA2} of Support Information gives further assistance to the interested reader.

\begin{table}[!h]
	\caption{.}
	\footnotesize
	\input{tables/tabPCA3MET}
\label{tab:min}
\end{table}

@@

    \subsection{Primitive typology from Erd\"os sectors}\label{sec:pty}
Such stability of activity along time, Erd\"os sector relative sizes, principal components formation and concentration of variance suggests that understanding types of networks and participants might benefit from a characterization within such framework.
We considered the most trivial case, in which the sector to which a participant belongs is regarded as her/his type. This is useful in deriving more elaborate typologies, and yield a sketch of or a ``primitive'' typology. General considerations:
\begin{itemize}
	\item A participant belongs to many networks (his family, family of a friend, the email list to which he belongs, work friends, etc.).
	\item A participant might belong to all three sectors at the same time. Actually, it is reasonable to assume that almost every person belongs to all three sectors for some of the networks.
	\item It is given by construction that a participant is of just one type at a network in a given snapshot (exception for the compound inclusive and exclusive criterion given in Section~\ref{sectioning}).
	\item The participant often transitions from one sector to another within a network.
	\item Reported stability of network structure arises from activity with continuous change of the participant types.
	\item Type often changes with the scale of the activity window. For example, two snapshots of 200 and 10000 messages will probably reveal participants with more than one type. 
\end{itemize}
